19Q1

### 2019-04-03 19Q1.Rmd

# Sample info from figshare
crispr_meta <- read.delim("./data_munging/19Q1/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(crispr_meta)[colnames(crispr_meta) == "CCLE_name"] <- "CCLE_Name"
```

@@

```{r, eval=FALSE}
crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
```

@@

```{r, eval=FALSE}
cn_seg <- read.delim("./data_munging/19Q1/copy_number_20190328.csv.gz", sep = ",")
tcga_pancan <- read.delim("~/Desktop/GDC-PANCAN.masked_cnv.tsv.gz", sep = "\t")

@@

ggplot(tcga_pancan, aes(x = value)) + 
  geom_density()
```

>>>>

tcga_hist_converter <- read.delim("./data_munging/TCGA/ge_cancer_map_20190403.csv", sep = ",")
tcga_hist_converter$Cell_line <- toupper(gsub("-", "", tcga_hist_converter$Cell_line))
tcga_hist_converter %>% count(TCGA_classification)
```

@@

```{r, eval=FALSE}
# Sample info from figshare
crispr_meta <- read.delim("./data_munging/19Q1/sample_info_20190306.csv", sep = ",", header = TRUE, na.strings = c("", NA))
colnames(crispr_meta)[colnames(crispr_meta) == "CCLE_name"] <- "CCLE_Name"

crispr <- read.delim("./data_munging/19Q1/gene_effect_corrected_20190305.csv.gz", sep = ",", check.names = FALSE, header = TRUE)
```

@@

```{r, eval=FALSE}
# Seg data is only for cell lines in teh CRISPR screen
cn_seg <- read.delim("./data_munging/19Q1/depmap_19Q1_cn_seg_20190403.csv", sep = ",")
cn_seg <- merge(select(ccl_histologies, Histology, Broad_ID), cn_seg, by = "Broad_ID", all.y = TRUE)

tcga_seg <- read.delim("./data_munging/TCGA/GDC-PANCAN.masked_cnv.ucscxena_seg_20190403.tsv.gz", sep = "\t")

@@

ggplot(tcga_seg, aes(x = value)) + 
  geom_density()
```
